\clearpage
\phantomsection
\addcontentsline{toc}{section}{ABSTRACT}
\section*{ABSTRACT}

Digital transformation in the Micro, Small, and Medium Enterprises (MSMEs) sector has become a crucial factor in increasing operational efficiency and market competitiveness. MSME Ice Tea faces challenges in managing transaction data and inventory monitoring, which are still conducted conventionally, posing a risk of data inaccuracy. This research aims to design and implement a web-based sales information system with key features of automated stock management and an analytical dashboard. The system development is built using the Laravel Framework based on PHP, implementing the MVC (Model-View-Controller) architecture for backend logic processing. This approach is chosen to enhance security, code organization, and system scalability. The frontend utilizes the Blade templating engine integrated with HTML, CSS, and JavaScript for the user interface. All operational data is integrated using MySQL database management system with Eloquent ORM features to ensure efficient and secure data manipulation. The research results indicate that the integration of online ordering features with automatic stock updates can minimize human error in inventory recording. Furthermore, the provided analytical dashboard assists business owners in monitoring real-time sales trends to support strategic decision-making. This report is expected to serve as a practical reference for the digitalization of business governance for MSME actors.

\textbf{Keywords}: MSME, Website, Laravel, MySQL, MVC, Automated Stock, Analytical Dashboard.
